\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2021-02-03 sections/methods.tex
Update manuscript to address comment R1.1

  \subsection*{Consensus Network and p-value merging}
  \vspace{-5mm}
  Fisher~\cite{fisher_224a_1948} proposed that for $k$ independent p-values, each generated by $k$ different methods and denoted by $P_i$, the statistic $\Psi$:
  \begin{equation*}
    \begin{aligned}
        \Psi &= \sum_{i=1}^k -2 \log \left( P_i \right) \\
        \Psi &\sim \chi^2_{2k}
    \end{aligned}
  \end{equation*}

@@

  The consensus method in \ac{micone} uses Equation~\ref{eqn:covariance-pvalues} to estimate the covariance of the pvalues and Equation~\ref{eqn:pvalue-combined} to merge the p-values (obtained from bootstrapping) from different methods. The combined p-values are used to threshold for significance during the consensus network step.

  \subsection*{Code and Data Availability}
  Pipeline: \href{https://github.com/segrelab/MiCoNE}{https://github.com/segrelab/MiCoNE} \\
  Data and scripts: \href{https://github.com/segrelab/MiCoNE-pipeline-paper}{https://github.com/segrelab/MiCoNE-pipeline-paper}

>>>>

  \subsection*{Consensus Network and p-value merging}
  \vspace{-5mm}

  \subsubsection*{Bootstrapping}
  For each network inference method (both correlation and direct association based methods), $1000$ permutations of the original \ac{otu} counts data were generated~\cite{Watts2018}.
  We then recalculate the associations in these permuted \ac{otu} tables using the different network inference algorithms.
  Finally, we calculate the p-value based on how often a more extreme association is observed for randomly permuted data.

  \subsubsection*{p-value merging}
  Fisher~\cite{fisher_224a_1948} proposed that for $k$ independent p-values, each generated by $k$ different methods and denoted by $P_i$, the statistic $\Psi$:
  \begin{equation*}
    \begin{aligned}
        \Psi &= \sum_{i=1}^k -2 \log \left( P_i \right) \\
        \Psi &\sim \chi^2_{2k}
    \end{aligned}
  \end{equation*}

@@

  The consensus method in \ac{micone} (refer Documentation) uses Equation~\ref{eqn:covariance-pvalues} to estimate the covariance of the pvalues and Equation~\ref{eqn:pvalue-combined} to merge the p-values (obtained from bootstrapping) from different methods. The combined p-values are used to threshold for significance during the consensus network step.

  \subsection*{Code and Data Availability}
  Pipeline: \href{https://github.com/segrelab/MiCoNE}{https://github.com/segrelab/MiCoNE} \\
  Documentation: \href{https://micone.readthedocs.io}{https://micone.readthedocs.io} \\
  Data and scripts: \href{https://github.com/segrelab/MiCoNE-pipeline-paper}{https://github.com/segrelab/MiCoNE-pipeline-paper}

### 2021-02-03 sections/results.tex
Update manuscript to address comment R1.1

  Unlike the previous steps of the pipeline, where were we evaluated the performance of methods on mock datasets, there is no equivalent dataset that contain a set of known interactions for the evaluation of the network inference algorithms.
  Therefore, we propose the construction of a consensus network (Figure~\ref{fig:figure5}C) involving \ac{magma}, \ac{mldm}, \ac{spieceasi} and \ac{sparcc}. This consensus network is built by merging the p-values generated from bootstraps of the original taxonomy composition table using the Browns p-value combining method~\cite{Poole} (see Methods section).
  Based on this approach, \ac{micone} reports as default output the consensus network, annotated with weights (correlations for \ac{sparcc} and direct associations for the other methods) for all four methods.

>>>>

  Unlike the previous steps of the pipeline, where were we evaluated the performance of methods on mock datasets, there is no equivalent dataset that contain a set of known interactions for the evaluation of the network inference algorithms.
  Therefore, we propose the construction of a consensus network (Figure~\ref{fig:figure5}C) involving \ac{magma}, \ac{mldm}, \ac{spieceasi} and \ac{sparcc}. This consensus network is built by merging the p-values generated from bootstraps of the original taxonomy counts table using the Browns p-value combining method~\cite{brown_400_1975} (see Methods section).
  Based on this approach, \ac{micone} reports as default output the consensus network, annotated with weights (correlations for \ac{sparcc} and direct associations for the other methods) for all four methods.
